---
title: "Prediction Student Acceptance"
author: "Hector Motsepe"
date: "08/09/2020"
output: html_document
---

```{r}
myData <- read.csv('https://stats.idre.ucla.edu/stat/data/binary.csv')
head(myData)
summary(myData)
str(myData)
myData$rank <- as.factor(myData$rank)
myData$admit <- as.factor(myData$admit)
```
# Alter data for purpose of tutorial (add one)
```{r}
myData[myData$admit == 1, 'gpa'] <- myData[myData$admit == 1, 'gpa'] + 1
```
# Plot the data
```{r}
library(tidyverse)
ggplot(myData, mapping = aes(x = gpa, y = admit)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)    +
  coord_cartesian(ylim = c(0, 1))

ggplot(myData, mapping = aes(x = gpa, y = admit)) +
  geom_point() +
  geom_smooth(method = "glm", se = FALSE, method.args = list(family = 'binomial'))    +
  coord_cartesian(ylim = c(0, 1))
```
# MODEL ADMIT BY GPA
```{r}
gpaModel <- glm(admit ~ gpa, data = myData, family = 'binomial')
gpaModel
exp(coef(gpaModel)) # increase in gpa the student is more likely to be accepted
exp(confint(gpaModel))
```
# Predict admit by gpa, gre, and rank

```{r}
full_Model <- glm(admit ~ gpa + log2(gre) + rank,
                  data = myData, family = 'binomial')
full_Model
exp(coef(full_Model)) # increase in gpa the student is more likely to be accepted
exp(confint(full_Model))
cbind(OR = exp(coef(full_Model)), exp(confint(full_Model)))
```

# Testing Overall contribution of Rank
```{r}
library(aod)
wald.test(b = coef(full_Model), Sigma = vcov(full_Model), Terms = 4:6) 
```
# RANK OF UNIVERSITY DOES NOT CONTRIBUTE TO OUR MODEL "REMOVE rank from OUR MODEL'
```{r}
final_full_Model <- glm(admit ~ gpa + log2(gre),
                  data = myData, family = 'binomial')

final_full_Model
exp(coef(final_full_Model)) # increase in gpa the student is more likely to be accepted
exp(confint(final_full_Model))
cbind(OR = exp(coef(final_full_Model)), exp(confint(final_full_Model)))
```

# ASSESSS MODEL USING CROSS VALIDATION
```{r}
library(caret)
```
# Give the method instructions
```{r}
crossValSettings <- trainControl(method = 'repeatedcv', number = 10,
                                 savePredictions = TRUE)

crossVal <- train(as.factor(admit) ~ gpa + log2(gre), data = myData, family ='binomial',
                  method = 'glm', trControl = crossValSettings)
crossVal

pred <- predict(crossVal, newdata = myData)
myData$admit <- as.factor(myData$admit) # make sure to change to factor
pred
confusionMatrix(data = pred, myData$admit)
```
# produce roc curve of model
```{r}
library(ROCR)
profFull <- predict(full_Model, myData, 'response')
profFull
predict_FULL <- prediction(profFull, myData$admit)
predict_FULL
performance_FULL <- performance(predict_FULL, measure = 'tpr', x.measure = 'fpr')

plot(performance_FULL, col='blue')

profGPA <- predict(gpaModel, myData, 'response')
profGPA
predict_GPA <- prediction(profGPA, myData$admit)
predict_GPA
performance_GPA <- performance(predict_GPA, measure = 'tpr', x.measure = 'fpr')

plot(performance_FULL, col='blue')
plot(performance_GPA, col='red', add = TRUE)

AUC_full <-  performance(predict_FULL, measure = 'auc')
AUC_gpa<-  performance(predict_GPA, measure = 'auc')
AUC_full@y.values
AUC_gpa@y.values
```

# BUILDING A MULTINOMIAL LOGISTIC REGRESSION
```{r}
data("iris")
summary(iris)

library(nnet)

multimodel <- multinom(Species ~ log2(Sepal.Width), data = iris)
summary(multimodel)
coef(multimodel)
1/ exp(coef(multimodel))[,2]

ggplot(iris, aes(Species, Sepal.Width)) +
  geom_boxplot()
```
